### 2011-05-11 paper.tex
worked on intersection lemma some more

Thus, in order to prove Theorem \ref{amplify}, we just need to show that any \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class is closed under majority reductions. In order to show that these are closed under majority reductions, we will need the help of another property:
\begin{definition}\label{defintersection}
We say that a class $C$ is \emph{closed under intersection} if for any language $L \in C$, the language $\intersection(L) = \{(x_1,...,x_k) : k\in\mathbb{N}, x_i \in L_i ~ \forall i\}$ is in $C$.
\end{definition}
We will demonstrate that all $\{\Sigma, \Pi, \bp, \parity\}$-constructible complexity classes are closed under intersection and under majority reductions. To do this, we will use induction on the number of operators in $C$. Clearly $\p$ is closed under intersection and majority reductions. Thus, the result follows from the following two lemmas:

@@

\begin{lemma}\label{amplifymainlemma}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. If $C$ is closed under majority reductions, then (i) \emph{$\Sigma \cdot C$}, (ii) \emph{$\Pi \cdot C$}, (iii) \emph{$\bp \cdot C$}, and (iv) \emph{$\parity \cdot C$} are all closed under majority reductions.
\end{lemma}
We begin with the proof of Lemma \ref{intersectionlemma}
\begin{proof} \emph{(Lemma \ref{intersectionlemma})}
\begin{enumerate}
\item[(i)] Suppose $L \in \Sigma\cdot C$. Then there exists a language $M\in C$ such that $x \in L$ if and only if there exists some $y$ (of length polynomial in the length of $x$) such that $(x, y)\in M$. Now, we want to construct a $\Sigma \cdot C$ machine for $\intersect(L)$; that is, given a $k$-tuple $(x_1,x_2,...,x_k)$, we want to determine if all $x_i$ are in $L$. To do this, we just guess a $k$-tuple $(y_1,y_2,...,y_k)$, and then check if $M$ accepts $(x_1, y_1)$, $(x_2, y_2)$, ..., and $(x_k, y_k)$. This is equivalent to checking that $((x_1,y_1),(x_2,y_2),...,(x_k,y_k)) \in \intersect(M)$, and by assumption, $\intersect(M)$ is in $C$ since $M$ is in $C$.

@@

\item[(iii)] Now we consider $\bp \cdot C$. By assumption, $C$ is closed under majority reductions, so by Lemma \ref{majorityimpliesamplify}, $\bp \cdot C = \strongbp \cdot C$. If we take any language $L \in \bp \cdot C$, we find that $L \in \strongbp \cdot C$. Therefore, there exists a $C$ machine $M$ such that $x\in L$ if and only if
\begin{center}
$\displaystyle \pr_y [M(x,y)\text{ accepts}] > $
\end{center}

\item[(iv)] Finally, we consider $\parity \cdot C$. If $L \in \parity \cdot C$, then there is a language $M \in C$ such that $x\in L$ if and only if an odd number of $(x,y)$ are in $M$, where, again, $y$ is polynomial length in the length of $x$. We want to show that $\intersect(L)$ is in $\parity \cdot C$. Say we have $x_1,x_2,...,x_k$ and we need to verify that all of them are in $L$. Then, guess $y_1,y_2,...,y_k$ and see if $((x_1,y_1),(x_2,y_2),...,(x_k,y_k))$ is in $\intersect(M)$. Accept if there are an odd number of sequences $y_1,y_2,...,y_k$ for which this accepts. To see why this works, let $\# x_i$ be the number of $y_i$ for which $(x_i, y_i) \in M$. Then, the number of sequences $y_1,y_2,...,y_k$ which will accept is equal to $(\# x_1)(\# x_2)...(\# x_k)$ which is odd if and only if $\# x_i$ is odd for all $i$.
\end{enumerate}
\end{proof}

>>>>

Thus, in order to prove Theorem \ref{amplify}, we just need to show that any $\{\Sigma,\Pi,\bp,\parity\}$-constructible complexity class is closed under majority reductions. In order to show that these are closed under majority reductions, we will need the help of another property:
\begin{definition}\label{defintersection}
We say that a class $C$ is \emph{closed under intersection} if for any language $L \in C$, the language $\intersection(L) = \{(x_1,...,x_k) : k\in\mathbb{N}, x_i \in L_i ~ \forall i\}$ is in $C$.
\end{definition}
We will demonstrate that all $\{\Sigma, \Pi, \bp, \parity\}$-constructible complexity classes are closed under intersection and under majority reductions. To do this, we will use induction on the number of operators in $C$. Clearly $\p$ is closed under intersection and majority reductions. Thus, the result follows from the following two lemmas:

@@

\begin{lemma}\label{amplifymainlemma}
Let $C$ be a \emph{$\{\Sigma,\Pi,\bp,\parity\}$}-constructible complexity class. If $C$ is closed under majority reductions, then (i) \emph{$\Sigma \cdot C$}, (ii) \emph{$\Pi \cdot C$}, (iii) \emph{$\bp \cdot C$}, and (iv) \emph{$\parity \cdot C$} are all closed under majority reductions.
\end{lemma}
We begin with the proof of Lemma \ref{intersectionlemma}
\begin{proof} \emph{(Lemma \ref{intersectionlemma})}
\begin{enumerate}
\item[(i)] Suppose $L \in \Sigma\cdot C$. Then there exists a language $M\in C$ and a polynomial $p$ such that $x \in L$ if and only if there exists some $y$ with $|y| = p(|x|)$ such that $(x, y)\in M$. Now, we want to construct a $\Sigma \cdot C$ machine for $\intersect(L)$; that is, given a $k$-tuple $(x_1,x_2,...,x_k)$, we want to determine if all $x_i$ are in $L$. To do this, we just guess a $k$-tuple $(y_1,y_2,...,y_k)$, and then check if $M$ accepts $(x_1, y_1)$, $(x_2, y_2)$, ..., and $(x_k, y_k)$. This is equivalent to checking that $((x_1,y_1),(x_2,y_2),...,(x_k,y_k)) \in \intersect(M)$, and by assumption, $\intersect(M)$ is in $C$ since $M$ is in $C$.

@@

%\item[(iii)] Now we consider $\bp \cdot C$. By assumption, $C$ is closed under majority reductions, so by Lemma \ref{majorityimpliesamplify}, $\bp \cdot C = \strongbp \cdot C$. If we take any language $L \in \bp \cdot C$, we find that $L \in \strongbp \cdot C$. Therefore, there exists a $C$ machine $M$ such that $x\in L$ if and only if
%\begin{center}
%$\displaystyle \pr_y [M(x,y)\text{ accepts}] > $
%\end{center}

\item[(iii)] Now we consider $\bp \cdot C$. Let $L$ be a language in $\bp \cdot C$. Then, there is some language $M \in C$ and a polynomial $p$ such that $\pr_y[(x,y) \in M] > 2/3$ if $x\in L$ and $\pr_y[(x,y) \not \in M] < 1/3$ if $x\not\in L$, where $y$ is chosen as a random string of length $p(|x|)$.

By assumption, $C$ is closed under majority reductions and under intersection. Thus,\linebreak $\intersect(\majority(M)) \in C$. We want to show that $\intersect(L) \in \bp\cdot C$. For any $(x_1,x_2,...,x_k)$, we randomly choose random strings $y_{i,j}$ of length $p(|x_i|)$, for $1\le i\le k$ and $j\le 1\le \ell$, where $\ell = \lceil 48\ln(3/2)k \rceil$. Then, we check if
\begin{center}
$((x_{1,1},x_{1,2},...,x_{1,\ell}),(x_{2,1},x_{2,2},...,x_{2,\ell}),...,(x_{k,1},x_{k,2},...,x_{k,\ell}))$
\end{center}
is in $\intersect(\majority(\ell))$.

\item[(iv)] Finally, we consider $\parity \cdot C$. If $L \in \parity \cdot C$, then there is a language $M \in C$ and a polynomial $p$ such that $x\in L$ if and only if an odd number of $(x,y)$ are in $M$ where $|y| = p(|x|)$. We want to show that $\intersect(L)$ is in $\parity \cdot C$. Say we have $x_1,x_2,...,x_k$ and we need to verify that all of them are in $L$. Then, guess $y_1,y_2,...,y_k$ and see if $((x_1,y_1),(x_2,y_2),...,(x_k,y_k))$ is in $\intersect(M)$. Accept if there are an odd number of sequences $y_1,y_2,...,y_k$ for which this accepts. To see why this works, let $\# x_i$ be the number of $y_i$ for which $(x_i, y_i) \in M$. Then, the number of sequences $y_1,y_2,...,y_k$ which will accept is equal to $(\# x_1)(\# x_2)...(\# x_k)$ which is odd if and only if $\# x_i$ is odd for all $i$.
\end{enumerate}
\end{proof}
